---
title: "R Notebook"
output: html_notebook
---

Packages

```{r}
library(data.table)
library(xtable)
library(stringr)
```

Official hierarchy

```{r}
hierachy <- fread("~/mac/nauka/oja-lab/job-ads-datasets/data/kzis-hierarchy-2023.tsv", colClasses = "character", sep = "\t")
hierachy6 <- hierachy[str_detect(class, "\\d{6}")]
head(hierachy, 10)
```

Table 3.1 from the paper

```{r}
hierachy[, .(digits2=uniqueN(substr(class[str_detect(class, "\\d{2}")], 1,2)),
             digits3=uniqueN(substr(class[str_detect(class, "\\d{3}")], 1,3)),
             digits4=uniqueN(substr(class[str_detect(class, "\\d{4}")], 1,4)),
             digits6=uniqueN(substr(class[str_detect(class, "\\d{6}")], 1,6)),
             digits6_no=uniqueN(substr(class[str_detect(class, "\\d{6}") & !str_detect(class, "90$")], 1,6)))
         , keyby=.(digit1=substr(class, 1, 1))] |>
  transform(digit1=factor(digit1, 0:9,
                          c("0 Armed forces", "1 Public authorities, senior officials and managers", "2 Professionals", 
                            "3 Technicians and associate professionals", "4 Clerical support workers", "5 Service and sales workers", 
                            "6 Farmers, gardeners, foresters and fishermen", "7 Craft and related trades workers", 
                            "8 Plant and machine operators and assemblers", "9 Blue collar workers"))) -> hierarchy_details

rbind(
  hierarchy_details,
  hierarchy_details[, lapply(.SD, sum), .SDcols = digits2:digits6_no][, digit1:="All"]
) |>
  xtable() |>
  print.xtable(include.rownames = F)
```

Read training and test datasets

```{r}
train_full <- fread("~/mac/nauka/oja-lab/job-ads-datasets/data/train-test/train-data-2024.tar.gz", colClasses = "character")
test_full <- fread("~/mac/nauka/oja-lab/job-ads-datasets/data/train-test/test-data-2024.tar.gz", colClasses = "character")

df_full <- rbind(train_full,test_full)
df_full[, .N]
```

General information on the data

```{r}
df_full[, .N, source][, id:=1] |>
  transform(source = factor(source, c("official", "info", "gus", "esco", "kprm", "hand", "hand1k", "cbop"))) |>
  dcast(id ~ source, value.var = "N") |>
  transform(id = NULL) |> 
  xtable() |>
  print.xtable(include.rownames = F, format.args = list(big.mark = ","))
```

Coverage of codes by sources and dataset (table 5.1)

```{r}
hierachy6[, esco :=  class %in% unique(df_full$class[df_full$source == "esco"])]
hierachy6[, gus :=  class %in% unique(df_full$class[df_full$source == "gus"])]
hierachy6[, info :=  class %in% unique(df_full$class[df_full$source == "info"])]
hierachy6[, kprm :=  class %in% unique(df_full$class[df_full$source == "kprm"])]
hierachy6[, hand :=  class %in% unique(df_full$class[df_full$source == "hand"])]
hierachy6[, hand1k :=  class %in% unique(df_full$class[df_full$source == "hand1k"])]
hierachy6[, cbop:= class %in% unique(df_full$class[df_full$source == "cbop"])]

hierachy6[, all := (esco + gus + info + kprm + hand + hand1k + cbop) > 0]

setcolorder(hierachy6, c("class", "name", "info", "gus", "esco", "kprm", "hand", "hand1k", "cbop", "all"))

hierachy6[, lapply(.SD, function(x) mean(x)*100),  keyby=.(digit1=substr(class,1,1)), .SDcols = info:all]|>
  transform(N = df_full[,.N, keyby=.(class=substr(class,1,1))]$N) |>
  xtable(digits=1) |>
  print.xtable(include.rownames = F, format.args = list(big.mark =","))
```


Number of cases for a given class

```{r}
df_full[,.N, class][, .(nrows=.N), keyby=N]
```


Which are not covered by data source

```{r}
hierachy6[all == FALSE, .N, .(d1=substr(class,1,1))]
```

Number of characters by main groups 

```{r}
df_full[, n_chars:= str_count(desc, "\\w+")]
```

Table words -- overall

```{r}
df_full[, as.list(summary(n_chars))] |>
  xtable(digits = 0) |>
  print.xtable(include.rownames = F, format.args = list(big.mark = ","))
```

Table words -- by group

```{r}
df_full[, as.list(summary(n_chars)), keyby=.(digit1=substr(class,1,1))] |>
  merge(x = _,
        y = df_full[,.N, keyby=.(digit1=substr(class,1,1))],
        by = "digit1") |>
  xtable(digits = 1) |>
  print.xtable(include.rownames = F, format.args = list(big.mark = ","))
```

Table for the appendix

```{r}
df_full[, as.list(summary(n_chars)), keyby=.(digit1=substr(class,1,1), source)]|>
    merge(x = _,
        y = df_full[,.N, keyby=.(digit1=substr(class,1,1), source)],
        by = c("digit1", "source")) |>
  xtable(digits = 1) |>
  print.xtable(include.rownames = F, format.args = list(big.mark = ","))
```


Information about the number of cases

```{r}
train_full[, .(train_cases=.N, train_codes=uniqueN(class)), source] |>
  merge(x = _,
        y = test_full[, .(test_cases=.N, test_codes=uniqueN(class)), source],
        by = "source",
        all = T) |>
  xtable(digits = 0) |>
  print.xtable(include.rownames = F, format.args = list(big.mark = ","))
```

```{r}
train_full[, .(train_cases=.N, train_codes=uniqueN(class))][, source:="All"] |>
  merge(x = _,
        y = test_full[, .(test_cases=.N, test_codes=uniqueN(class))][, source:="All"],
        by = "source",
        all = T) |>
  xtable(digits = 0) |>
  print.xtable(include.rownames = F, format.args = list(big.mark = ","))
```

```{r}
train_full[source %in% c("hand", "hand1k"), .N, keyby=.(code = substr(class,1,1))]
test_full[source %in% c("hand", "hand1k"), .N, keyby=.(code = substr(class,1,1))]
```

