---
title: "R Notebook"
output: html_notebook
---

```{r}
library(reticulate)
library(stringr)
library(data.table)
library(ggplot2)
library(xtable)
library(ggh4x)
library(countrycode)
library(openxlsx)
library(forcats)
```


```{r}
measures <- c('acc/recall@1', 'macro_acc', 'recall@2', 'recall@3', 'recall@4',
       'recall@5', 'recall@6', 'recall@7', 'recall@8', 'recall@9', 'log-loss',
       'mse_pred_dist', 'mse_single_pred_dist', 'recall@10', 'acc/recall@1',
       'macro_acc', 'recall@2', 'recall@3', 'recall@4', 'recall@5', 'recall@6',
       'recall@7', 'recall@8', 'recall@9', 'log-loss', 'mse_pred_dist',
       'mse_single_pred_dist', 'recall@10')
```

Linear models results

```{r}
linear_results <- py_load_object("../results/NAWA-linear-results.pickle", convert = T)
linear_results <- lapply(linear_results, rbindlist)
linear_results$overall
linear_results <- lapply(linear_results, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("lin_top", "lin_bot"), each = 56/2)]
    }
  else {
    x[, measure:=rep(measures, times = 1)]
    x[, model:=rep(c("lin_top", "lin_bot"), each = 28/2)]
  }
  })

linear_results_df <- rbindlist(linear_results, idcol = "dataset")
linear_results_df <- linear_results_df[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
linear_results_df[, measure:=str_remove(measure, "acc/")]

linear_results_df[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     model = factor(model, c("lin_bot", "lin_top"), c("Logistic(bottom)", "Logistic(top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(linear_results_df, c("dataset", "type", "model", "measure"))
setnames(linear_results_df, paste("level", 0:4), paste0("level", 0:4))
setcolorder(linear_results_df, c("dataset", "type", "model", "measure"))
```

Transformer results for Polish language


```{r}
transformer_results <- py_load_object("../results/NAWA-trans-base-results.pickle", convert = T)
transformer_results <- lapply(transformer_results, rbindlist)
transformer_results <- lapply(transformer_results, \(x) { 
  if (nrow(x) == 112) {
    x[, measure:=rep(measures, times = 4)]
    x[, model:=rep(c("tra_top", "tra_top_rob", "tra_bot", "tra_bot_rob"), each = 112/4)]
    }
  else {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top", "tra_top_rob", "tra_bot", "tra_bot_rob"), each = 56/4)]
  }
  })

transformer_results_df <- rbindlist(transformer_results, idcol = "dataset")
transformer_results_df <- transformer_results_df[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
transformer_results_df[, measure:=str_remove(measure, "acc/")]

transformer_results_df[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     model = factor(model, c("tra_bot", "tra_top", "tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(bottom)", "Transformer(top)", "Transformer(rob,bottom)", "Transformer(rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(transformer_results_df, c("dataset", "type", "model", "measure"))
setnames(transformer_results_df, paste("level", 0:4), paste0("level", 0:4))
setcolorder(transformer_results_df, c("dataset", "type", "model", "measure"))
```

Transformer (large) results for Polish

```{r}
transformer_large_results <- py_load_object("../results/NAWA-trans-large-results.pickle", convert = T)
transformer_large_results <- lapply(transformer_large_results, rbindlist)
transformer_large_results
transformer_large_results <- lapply(transformer_large_results, \(x) { 
  if (nrow(x) == 112) {
    x[, measure:=rep(measures, times = 4)]
    x[, model:=rep(c("tra_top", "tra_top_rob", "tra_bot", "tra_bot_rob"), each = 112/4)]
    }
  else {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top", "tra_top_rob", "tra_bot", "tra_bot_rob"), each = 56/4)]
  }
  })

transformer_large_results_df <- rbindlist(transformer_large_results, idcol = "dataset")
transformer_large_results_df <- transformer_large_results_df[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
transformer_large_results_df[, measure:=str_remove(measure, "acc/")]

transformer_large_results_df[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     model = factor(model, c("tra_bot", "tra_top", "tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(large,bottom)", "Transformer(large,top)",
                                      "Transformer(large,rob,bottom)","Transformer(large,rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(transformer_large_results_df, c("dataset", "type", "model", "measure"))
setnames(transformer_large_results_df, paste("level", 0:4), paste0("level", 0:4))
setcolorder(transformer_large_results_df, c("dataset", "type", "model", "measure"))
```

Data for plot fig1-recall1.pdf

```{r}
rbind(linear_results_df, transformer_results_df, transformer_large_results_df) |>
  melt(id.vars = c("dataset", "type", "model", "measure")) |>
  subset(dataset %in% c("Overall", "ePraca", "Hand-coded") 
         & measure %in% c("recall@1") 
         & type == "Test dataset"
         )  |>
  transform(variable = factor(variable, paste0("level", 0:4), 
                           c("1 digit", "2 digits", "3 digits", "4 digits\nISCO", "6 digits")),
            model = factor(model, 
                           levels = c("Logistic(bottom)", "Logistic(top)", 
                                      "Transformer(bottom)", "Transformer(top)", 
                                      "Transformer(rob,bottom)", "Transformer(rob,top)", 
                                      "Transformer(large,bottom)", "Transformer(large,top)", 
                                      "Transformer(large,rob,bottom)", "Transformer(large,rob,top)"),
                           labels = c("Linear, bottom-up", "Linear, top-down", 
                                      "Transformer (HerBERT-base), bottom-up", "Transformer (HerBERT-base), top-down", 
                                      "Transformer (XLM-RoBERTa-base), bottom-up", "Transformer (XLM-RoBERTa-base), top-down", 
                                      "Transformer (HerBERT-large), bottom-up", "Transformer (HerBERT-large), top-down", 
                                      "Transformer (XLM-RoBERTa-large), bottom-up", "Transformer (XLM-RoBERTa-large), top-down"
                                      ))) -> data_for_plot
  

ggplot(data = data_for_plot, aes(x = variable, 
                       y = value, 
                       group = model, 
                       fill = model)) +
  geom_col(position = "dodge", color = "black") +
  geom_text(aes(label = scales::percent(value, scale=1,accuracy = 0.1,suffix="")), 
            position = position_dodge(width = 0.9), 
            vjust = 0.5,
            hjust = -0.25,
            size = 1.75,
            angle = 0) + 
  facet_nested_wrap(~dataset, ncol = 2) +
  scale_fill_brewer(type = "qual", palette = "Paired") +
  scale_x_discrete(limits = rev(levels(data_for_plot$variable))) +
  scale_y_continuous(breaks = seq(0,90,10)) + 
  labs(x = "Occupation digit", y = "Accuracy (Recall@1)", fill = "Classifier") +
  theme(legend.position = c(1, 0.5), legend.justification = c(1.25, 1.25)) +
  coord_flip() + 
  guides(fill = guide_legend(reverse = TRUE)) -> p1

ggsave(plot=p1,filename = "../figs/fig1-recall1.pdf", width = 12, height = 12)
ggsave(plot=p1,filename = "../figs/fig1-recall1.jpeg", width = 12, height = 12)
```

Separate plots

```{r}
dataset_l <- c("Overall", "ePraca", "Hand-coded")

for (level in dataset_l) {
  data_for_plot |>
  subset(dataset == level) |>
  ggplot(data = _, aes(x = variable, 
                       y = value, 
                       group = model, 
                       fill = model)) +
  geom_col(position = "dodge", color = "black") +
  geom_text(aes(label = scales::percent(value, scale=1,accuracy = 0.1,suffix="")), 
            position = position_dodge(width = 0.9), 
            vjust = 0.5,
            hjust = -0.25,
            size = 4,
            angle = 0) + 
  scale_fill_brewer(type = "qual", palette = "Paired") +
  scale_x_discrete(limits = rev(levels(data_for_plot$variable))) +
  scale_y_continuous(breaks = seq(0,90,10)) + 
  labs(x = "Occupation digit", y = "Accuracy (Recall@1)", fill = "Classifier") +
  theme(legend.position = "bottom", text=element_text(size = 15)) +
  coord_flip() + 
  guides(fill = guide_legend(reverse = TRUE, nrow = 4))  -> p1

  ggsave(plot=p1,
       filename = glue::glue("../figs/fig1-recall1-{tolower(level)}.pdf"), width = 12, height = 12)
  ggsave(plot=p1,
       filename = glue::glue("../figs/fig1-recall1-{tolower(level)}.jpeg"), width = 12, height = 12)
}


```



## Multilingual model and data (English and Polish)

```{r}
multi_polish <- py_load_object("../results/NAWA-trans-multi-pl-results-google.pickle", convert = T)
multi_polish <- lapply(multi_polish, rbindlist)
multi_polish <- lapply(multi_polish, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
    }
  else {
    x[, measure:=rep(measures, times = 1)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  }
  })

multi_polish <- rbindlist(multi_polish, idcol = "dataset")
multi_polish <- multi_polish[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multi_polish[, measure:=str_remove(measure, "acc/")]

multi_polish[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     language = "Polish", 
                     model = factor(model, c("tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(rob,bottom)", "Transformer(rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(multi_polish, c("language", "dataset", "type", "model", "measure"))
setnames(multi_polish, paste("level", 0:4), paste0("level", 0:4))
setcolorder(multi_polish, c("language", "dataset", "type", "model", "measure"))

multi_english <- py_load_object("../results/NAWA-trans-multi-en-results-google.pickle", convert = T)
multi_english <- lapply(multi_english, rbindlist)
multi_english <- lapply(multi_english, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
    }
  else {
    x[, measure:=rep(measures, times = 1)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  }
  })

multi_english <- rbindlist(multi_english, idcol = "dataset")
multi_english <- multi_english[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multi_english[, measure:=str_remove(measure, "acc/")]

multi_english[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     language = "English", 
                     model = factor(model, c("tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(rob,bottom)", "Transformer(rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(multi_english, c("language", "dataset", "type", "model", "measure"))
setnames(multi_english, paste("level", 0:4), paste0("level", 0:4))
setcolorder(multi_english, c("language", "dataset", "type", "model", "measure"))
```

Argos translations

```{r}
multi_polish_arg <- py_load_object("../results/NAWA-trans-multi-pl-results-argos.pickle", convert = T)
multi_polish_arg <- lapply(multi_polish_arg, rbindlist)
multi_polish_arg <- lapply(multi_polish_arg, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
    }
  else {
    x[, measure:=rep(measures, times = 1)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  }
  })

multi_polish_arg <- rbindlist(multi_polish_arg, idcol = "dataset")
multi_polish_arg <- multi_polish_arg[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multi_polish_arg[, measure:=str_remove(measure, "acc/")]

multi_polish_arg[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     language = "Polish", 
                     model = factor(model, c("tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(rob,bottom)", "Transformer(rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(multi_polish_arg, c("language", "dataset", "type", "model", "measure"))
setnames(multi_polish_arg, paste("level", 0:4), paste0("level", 0:4))
setcolorder(multi_polish_arg, c("language", "dataset", "type", "model", "measure"))

multi_english_arg <- py_load_object("../results/NAWA-trans-multi-en-results-argos.pickle", convert = T)
multi_english_arg <- lapply(multi_english_arg, rbindlist)
multi_english_arg <- lapply(multi_english_arg, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
    }
  else {
    x[, measure:=rep(measures, times = 1)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  }
  })

multi_english_arg <- rbindlist(multi_english_arg, idcol = "dataset")
multi_english_arg <- multi_english_arg[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multi_english_arg[, measure:=str_remove(measure, "acc/")]

multi_english_arg[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     language = "English", 
                     model = factor(model, c("tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(rob,bottom)", "Transformer(rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(multi_english_arg, c("language", "dataset", "type", "model", "measure"))
setnames(multi_english_arg, paste("level", 0:4), paste0("level", 0:4))
setcolorder(multi_english_arg, c("language", "dataset", "type", "model", "measure"))
```

```{r}
multi_english_her <- py_load_object("../results/NAWA-trans-multi-en-herbert-results.pickle", convert = T)
multi_english_her <- lapply(multi_english_her, rbindlist)
multi_english_her <- lapply(multi_english_her, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
    }
  else {
    x[, measure:=measures]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  }
  })

multi_english_her <- rbindlist(multi_english_her, idcol = "dataset")
multi_english_her <- multi_english_her[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multi_english_her[, measure:=str_remove(measure, "acc/")]

multi_english_her[, ":="(dataset = factor(dataset, 
                                          c("overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                                          c("Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     language = "English", 
                     model = factor(model, c("tra_bot_rob", "tra_top_rob"), 
                                    c("Transformer(rob,bottom,her)", "Transformer(rob,top,her)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

setorderv(multi_english_her, c("language", "dataset", "type", "model", "measure"))
setnames(multi_english_her, paste("level", 0:4), paste0("level", 0:4))
setcolorder(multi_english_her, c("language", "dataset", "type", "model", "measure"))
```


Plotting fig2-recall1.pdf

```{r}
rbind(multi_polish[, trans:="Google"], multi_english[, trans:="Google"], 
      multi_polish_arg[, trans:="Argos"], multi_english_arg[, trans:="Argos"],
      multi_english_her[, trans:=""],
      transformer_results_df[model %in% c("Transformer(bottom)", "Transformer(top)")][, trans:=""][, language:="Polish"]) |>
  melt(id.vars = c("trans", "language", "dataset", "type", "model", "measure")) |>
  subset(dataset %in% c("Overall", "ePraca", "Hand-coded") 
         & measure %in% c("recall@1") 
         & type == "Test dataset"
         )  |>
  transform(model= paste0(model, " (", trans, ")")) |>
  transform(variable = factor(variable, paste0("level", 0:4), 
                              c("1 digit", "2 digits", "3 digits", "4 digits\nISCO", "6 digits")),
            model = factor(model, 
                           levels = c("Transformer(rob,bottom) (Google)", 
                                      "Transformer(rob,top) (Google)", 
                                      "Transformer(rob,bottom) (Argos)", 
                                      "Transformer(rob,top) (Argos)", 
                                      "Transformer(bottom) ()",
                                      "Transformer(rob,bottom,her) ()", 
                                      "Transformer(top) ()",
                                      "Transformer(rob,top,her) ()"),
                           labels = c("Transformer (XLM-RoBERTa-base), bottom-up (Google)", 
                                      "Transformer (XLM-RoBERTa-base), top-down (Google)", 
                                      "Transformer (XLM-RoBERTa-base), bottom-up (Argos)", 
                                      "Transformer (XLM-RoBERTa-base), top-down (Argos)", 
                                      "Transformer (HerBERT-base), bottom-up", 
                                      "Transformer (HerBERT-base), bottom-up", 
                                      "Transformer (HerBERT-base), top-down",
                                      "Transformer (HerBERT-base), top-down"))) -> data_for_plot
  

data_for_plot |> 
ggplot(data = _, aes(x = variable, 
                       y = value, 
                       group = model, 
                       fill = model)) +
  geom_col(position = "dodge", color = "black") +
  geom_text(aes(label = scales::percent(value, scale=1,accuracy = 0.1,suffix="")), 
            position = position_dodge(width = 0.9), 
            vjust = 0.5,
            size = 5,
            hjust = -0.25,
            angle = 0) + 
  facet_nested_wrap(~language+dataset) +
  scale_fill_brewer(type = "qual", palette = "Paired") +
  scale_x_discrete(limits = rev(levels(data_for_plot$variable))) +
  scale_y_continuous(breaks = seq(0,110,10),
                     limits = c(0,100)) + 
  labs(x = "Occupation digit", y = "Accuracy (Recall@1)", fill = "Classifier") +
  #theme(legend.position = c(1, 0.5), legend.justification = c(1.25, 1.25)) +
  theme(legend.position = "bottom", text=element_text(size = 15)) +
  coord_flip()  + 
  guides(fill = guide_legend(reverse = TRUE, nrow = 3)) -> p2

ggsave(plot=p2,filename = "../figs/fig2-recall1.pdf", width = 13, height = 17)
ggsave(plot=p2,filename = "../figs/fig2-recall1.jpeg", width = 13, height = 17)

```



## Results for multilang dataset (hand only)

```{r}
multilang_overall <- py_load_object("../results/NAWA-trans-multi-overall.pickle", convert = T)
multilang_overall <- lapply(multilang_overall, rbindlist)
multilang_overall <- lapply(multilang_overall, \(x) { 
  if (nrow(x) == 56) {
    x[, measure:=rep(measures, times = 2)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
    }
  else {
    x[, measure:=rep(measures, times = 1)]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  }
  })

multilang_overall <- rbindlist(multilang_overall, idcol = "dataset")
multilang_overall <- multilang_overall[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multilang_overall[, measure:=str_remove(measure, "acc/")]
```

Table 
```{r}
multilang_overall[measure == "recall@1" & type == "test" & dataset %in% c("overall", "cbop", "hand")][
  , .(dataset, model, digit1=`level 0`, digit2=`level 1`, isco=`level 3`, kzis=`level 4`)] |>
  xtable() |>
  print.xtable(include.rownames = F)
```

Hand-coded data only (whole dataset)

```{r}
multilang <- py_load_object("../results/NAWA-trans-multi-hand.pickle", convert = T)
multilang <- lapply(multilang, rbindlist)
multilang <- lapply(multilang, \(x) { 
    x[, measure:=measures]
    x[, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 28/2)]
  })

multilang <- rbindlist(multilang, idcol = "dataset")
multilang <- multilang[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multilang[, measure:=str_remove(measure, "acc/")]
multilang[, lang:=str_extract(dataset, "[a-z]{2}\\.")]
multilang[, lang:=str_remove(lang, fixed("."))]
```

Test data (sample only)

```{r}
multilang_langs <- py_load_object("../results/NAWA-trans-multi-overall-lang.pickle", convert = T)

for (i in 1:length(multilang_langs)) {
  for (j in 1:3) {
    multilang_langs[[i]][[j]] <- rbindlist(multilang_langs[[i]][[j]])
    multilang_langs[[i]][[j]][, measure:=rep(measures, times = 2)]
    multilang_langs[[i]][[j]][, model:=rep(c("tra_top_rob", "tra_bot_rob"), each = 56/2)]
  }
  }


multilang_langs <- lapply(multilang_langs, rbindlist, idcol = "dataset")

multilang_langs <- rbindlist(multilang_langs, idcol = "lang")
multilang_langs <- multilang_langs[str_detect(measure, "recall\\@(1|2|3|4|5)$|log|macro")]
multilang_langs[, measure:=str_remove(measure, "acc/")]
multilang_langs[, lang:=str_extract(lang, "[a-z]{2}\\.")]
multilang_langs[, lang:=str_remove(lang, fixed("."))]
```


```{r}
multilang_for_plot_sample <- multilang_langs[measure == "recall@1" & dataset == "hand" & type == "test", 
                                .(digits1=`level 0`, digits4=`level 3`, digits6=`level 4`), 
                                .(model = factor(model, c("tra_bot_rob", "tra_top_rob"), c("bottom-up", "top-down")),
                                  lang = factor(lang, 
                                                c("bg", "cs", "da", "de", "el", "en", "es", "et", "fi", "fr", 
                    "ga", "hu", "it", "lt", "lv", "nl", "pl", "pt", "ro", "ru", 
                    "sk", "sl", "sv", "uk"),
                                                c("Bulgarian", "Czech", "Danish", "German", "Greek", "English",
                   "Spanish", "Estonian", "Finnish", "French", "Irish", "Hungarian",
                   "Italian", "Lithuanian", "Latvian", "Dutch", "Polish", 
                   "Portuguese", "Romanian", "Russian", "Slovak", "Slovenian",
                   "Swedish", "Ukrainian")))] |>
  melt(id.vars = c("model", "lang")) |>
  transform(variable = factor(variable, c("digits1", "digits4", "digits6"), c("1 digit", "4 digits\nISCO", "6 digits\nKZiS")),
            sample = "sample")

multilang_for_plot_whole <- multilang[measure == "recall@1", 
                                .(digits1=`level 0`, digits4=`level 3`, digits6=`level 4`), 
                                .(model = factor(model, c("tra_bot_rob", "tra_top_rob"), c("bottom-up", "top-down")),
                                  lang = factor(lang, 
                                                c("bg", "cs", "da", "de", "el", "en", "es", "et", "fi", "fr", 
                    "ga", "hu", "it", "lt", "lv", "nl", "pl", "pt", "ro", "ru", 
                    "sk", "sl", "sv", "uk"),
                                                c("Bulgarian", "Czech", "Danish", "German", "Greek", "English",
                   "Spanish", "Estonian", "Finnish", "French", "Irish", "Hungarian",
                   "Italian", "Lithuanian", "Latvian", "Dutch", "Polish", 
                   "Portuguese", "Romanian", "Russian", "Slovak", "Slovenian",
                   "Swedish", "Ukrainian")))] |>
  melt(id.vars = c("model", "lang")) |>
  transform(variable = factor(variable, c("digits1", "digits4", "digits6"), c("1 digit", "4 digits\nISCO", "6 digits\nKZiS")),
            sample = "whole")

multilang_for_plot <- rbind(multilang_for_plot_sample, multilang_for_plot_whole) |>
  transform(sample = factor(sample, c("whole", "sample"), c("Whole test dataset", "Sample only")))

factor_orders <- as.character(multilang_for_plot[sample == "Whole test dataset" & variable == "6 digits\nKZiS" & model=="bottom-up"][order(-value)]$lang)
```


Figure for multilingual

```{r}
multilang_for_plot |>
  transform(lang = factor(lang, factor_orders)) |>
  ggplot(data = _, aes(x = lang, y = value, color = variable, shape = model)) +
  geom_point(size = 2.5) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  scale_color_brewer(type = "qual", palette = "Set1")  +
  #scale_y_continuous(breaks = seq(0, 100, 5), limits = c(45, 85)) +
  labs(shape = "Approach", color = "Occupation\ncode", x = "", y = "Recall @1") +
  facet_wrap(~sample, ncol = 2)-> p_multi

ggsave(plot = p_multi, file = "../figs/fig-multi-recall.pdf", width = 10)
ggsave(plot = p_multi, file = "../figs/fig-multi-recall.jpeg", width = 10)
```

Data for Excel report

```{r}
tab1 <- rbind(linear_results_df, transformer_results_df, transformer_large_results_df)
setnames(tab1, names(tab1)[5:9], c("occup-1-digit", "occup-2-digits", "occup-3-digits", "occup-4-digits", "occup-6-digits"))
setorderv(tab1, c("dataset", "type", "model", "measure"))

tab2 <- rbind(multi_polish[, trans:="Google"], 
              multi_english[, trans:="Google"], 
              multi_polish_arg[, trans:="Argos"], 
              multi_english_arg[, trans:="Argos"],
              multi_english_her[, trans:="Herbert"],
              transformer_results_df[model %in% c("Transformer(bottom)", "Transformer(top)")][, trans:="Herbert"][, language:="Polish"])
setcolorder(tab2, c("trans", "language", "dataset", "type", "model", "measure"))
setorderv(tab2, c("trans", "language", "dataset", "type", "model", "measure"))

tab3 <- rbind(multilang,multilang_overall,multilang_langs, fill = T)
setcolorder(tab3, c("lang", "dataset", "type", "model", "measure"))
tab3[str_detect(dataset, "test-data"), dataset:="Sample"]

tab3[, ":="(dataset = factor(dataset, 
                             c("Sample", "overall", "cbop", "hand", "esco", "info",  "kprm", "official", "gus"),
                             c("Sample(test)", " Overall", "ePraca", "Hand-coded", "ESCO", "Info+",  "KPRM", "OfficialDict", "Thesaurus")),
                     type = factor(type, c("train", "test"), c("Train dataset", "Test dataset")),
                     model = factor(model, c("tra_bot_rob", "tra_top_rob"), c("Transformer(rob,bottom)", "Transformer(rob,top)")),
                     measure = factor(measure, c("recall@1", "recall@2", "recall@3", "recall@4", "recall@5", "log-loss", "macro_acc")))]

tab3[is.na(lang), lang := "All"]
tab3[, lang := factor(lang, 
                      c("All", "bg", "cs", "da", "de", "el", "en", "es", "et", "fi", "fr", 
                    "ga", "hu", "it", "lt", "lv", "nl", "pl", "pt", "ro", "ru", 
                    "sk", "sl", "sv", "uk"),
                    c("All languages", "Bulgarian", "Czech", "Danish", "German", "Greek", "English",
                   "Spanish", "Estonian", "Finnish", "French", "Irish", "Hungarian",
                   "Italian", "Lithuanian", "Latvian", "Dutch", "Polish", 
                   "Portuguese", "Romanian", "Russian", "Slovak", "Slovenian",
                   "Swedish", "Ukrainian"))]
setnames(tab3, names(tab3)[6:10], c("occup-1-digit", "occup-2-digits", "occup-3-digits", "occup-4-digits", "occup-6-digits"))
setorderv(tab3, c("lang", "dataset", "type", "model", "measure"))

```


Save reports to excel

```{r}
options("openxlsx.numFmt" = "0.0000")
options("openxlsx.withFilter" = TRUE)
options("keepNA" = TRUE)

excel_results <- createWorkbook(creator =  "Maciej Beręsewicz", 
                                title = "Results for the paper 'Multilingual hierarchical classification of job advertisements for job vacancy statistics'")

addWorksheet(excel_results, "Description")
writeData(wb = excel_results,
          sheet = "Description",
          x = data.frame(README = c("Dataset contains the following sheets:",
                                 "1. Polish-lang-only -- results for models for Polish data only",
                                 "2. Bilingual -- results for bilingual models (Polish and English)",
                                 "3. Multilingual -- results for 24 languages")),
          startCol = 3,
          startRow = 3, headerStyle = createStyle(textDecoration = "Bold"))


addWorksheet(excel_results, "Polish-lang-only")
writeData(wb = excel_results, 
          x=tab1, 
          sheet = "Polish-lang-only")

addWorksheet(excel_results, "Bilingual")
writeData(wb = excel_results, 
          x=tab2, 
          sheet = "Bilingual")

addWorksheet(excel_results, "Multilingual")
writeData(wb = excel_results, 
          x=tab3, 
          sheet = "Multilingual")

saveWorkbook(excel_results, file = "../results/models-accuracy.xlsx", overwrite = T)
```


```{r}
# Create dataframe with accuracy scores
accuracy_df <- data.frame(
  language = c("Greek", "German", "Irish", "Latvian", "Czech", "Slovenian", 
               "Hungarian", "Spanish", "Ukrainian", "Bulgarian", "Russian", 
               "French", "Portuguese", "Danish", "Finnish", "Swedish", "Dutch",
               "Romanian", "Italian", "Estonian", "Lithuanian", "Slovak", 
               "Polish", "English"),
  accuracy = c(77.14, 79.10, 75.65, 78.23, 79.54, 78.26, 78.29, 77.88, 
               76.44, 78.39, 77.82, 78.99, 78.34, 78.69, 77.17, 79.48, 
               79.16, 79.21, 77.03, 79.35, 78.80, 79.81, 79.55, 79.77)
)

# Create dataframe with roberta information
roberta_df <- data.frame(
  language = c("Bulgarian", "Czech", "Danish", "German", "Greek", "English", 
               "Spanish", "Estonian", "Finnish", "French", "Irish", "Hungarian",
               "Italian", "Lithuanian", "Latvian", "Dutch", "Polish", 
               "Portuguese", "Romanian", "Russian", "Slovak", "Slovenian",
               "Swedish", "Ukrainian"),
  train = c(12.3, 13.3, 15.4, 15.7, 14.5, 14.2, 16.0, 16.5, 14.6, 18.8, 
            14.2, 15.0, 12.2, 13.8, 14.4, 12.9, 12.2, 14.4, 12.3, 12.5, 
            16.4, 13.4, 14.1, 14.4),
  test = c(7.7, 11.1, 7.4, 8.0, 8.3, 9.3, 7.9, 7.7, 7.9, 11.3, 8.0, 9.3, 
           7.6, 7.2, 8.1, 7.6, 7.3, 10.2, 9.8, 9.5, 10.5, 8.2, 10.2, 7.8),
  roberta_tokens = c(5.5, 2.5, 7.8, 10.3, 4.3, 55.6, 9.4, 0.8, 6.7, 9.8, 
                     0.1, 7.8, 5.0, 1.8, 1.2, 5.0, 6.5, 8.4, 10.4, 23.4, 
                     3.5, 1.7, 0.1, 0.0),
  roberta_share = c(4.4, 2.0, 6.2, 8.2, 3.4, 44.3, 7.5, 0.7, 5.4, 7.8, 
                    0.1, 6.2, 4.0, 1.5, 1.0, 4.0, 5.2, 6.7, 8.3, 18.7, 
                    2.8, 1.3, 0.1, 0.0)
)

# Merge the dataframes
final_df <- merge(accuracy_df, roberta_df, by = "language")

# Order columns as desired
final_df <- final_df[, c("language", "accuracy", "train", "test", 
                        "roberta_tokens", "roberta_share")]

# View the first few rows
head(final_df)
```

```{r}
cor(final_df$train, final_df$accuracy, m = "s")
cor(final_df$train, final_df$accuracy, m = "p")

cor(final_df$test, final_df$accuracy, m = "s")
cor(final_df$test, final_df$accuracy, m = "p")

cor(final_df$roberta_tokens, final_df$accuracy, m = "s")
cor(final_df$roberta_tokens, final_df$accuracy, m = "p")

```

